\bf Faster Neural Machine Translation Inference

### 2018-01-31 fast-beam/fast-beam.tex
fast beam paper

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into acccount variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, target sentence lengths will still differ even for similar length inputs, compromising decoding performance. Figure~\ref{fig:batch-size} shows the actual batch size during decoding with a maximum batch size of 128; the batch was full in only 42\% of decoding iterations.

@@

We will propose an alternative batching algorithm to increase the actual batch size during decoding.

>>>>

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into acccount variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, maxi-batching can introduce unacceptable delay in response for online applications as the input are not processed in the order they came. It is also not appropriate for applications where only the output lengths varies, for example, image captioning.

Even with sequence-to-sequence NMT models, target sentence lengths will still differ even for similar length inputs, compromising decoding performance. Figure~\ref{fig:batch-size} shows the actual batch size during decoding with a maximum batch size of 128; the batch was full in only 42\% of decoding iterations.

@@

We will propose an alternative batching algorithm to increase the actual batch size during decoding without the problems associated with mini-batching and maxi-batching.
